---
title: "my xaringan slides"
output: 
  xaringan::moon_reader:
    nature:
      highlightStyle: github
      highlightLines: true
  
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
options(knitr.table.format = "html")
library(knitr)
library(tidyverse)
library(kableExtra)
library(DT)
```


# Introduce Yourself!

> My name is Eugene

---
class: bottom, right

# Change the alignment

to bottom and right

*All the details*

.left[left justified text]

???
presenter notes

---
class: middle
# Insert an image

using markdown notation
![image of momtocat](http://bit.ly/momtocat)

---
# Insert another image

using HTML

<img src="http://bit.ly/wiki-toddy" width="15%" align="right" />

---
# Incremental slides (one line)

Hello 
--
my name is Eugene 
--
I like sushi 

---
# Incremental slides (down a line)

Hello

--

my name is Eugene

--

I like sushi

---
# Two Columns

.pull-left[left side text]

.pull-right[right side text]

---
# add a table

```{r my_table}
head(iris) %>% 
  kable(format = "html") #<<
```

---
# add a plot
.pull-left[
```{r myplot, fig.retina=3, fig.show = 'hide'}
iris %>% 
  ggplot(aes(x=Sepal.Length, y=Sepal.Width, colour = Species)) +
  geom_point()
```
]

.pull-right[
```{r ref.label = 'myplot', echo=FALSE}
```
]

---
class: middle, inverse
background-image: url(http://bit.ly/arm-greens)

# Background image


---
class: middle, center, inverse
background-image: url(http://bit.ly/arm-greens)
background-size: cover

# Background image 'cover'


---
class: middle, right, inverse
background-image: url(http://bit.ly/arm-greens)
background-size: contain
background-position: center bottom

# background image position